### 2023-10-27 README.qmd
Add package citation info in README and render with tar_make()

# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" alt="" width="120" />

@@

> Note that the manuscript source-code for *Gould et al.* is located in a separate repository at [https://github.com/egouldo/ManyAnalysts](https://github.com/egouldo/ManyAnalysts), which can be viewed at [https://egouldo.github.io/ManyAnalysts/](https://egouldo.github.io/ManyAnalysts/).

@@

The data processing and analysis can be freely reproduced with the help of the [`targets::`](https://github.com/ropensci/targets) package. Please see the documentation at [https://docs.ropensci.org/targets/](https://docs.ropensci.org/targets/) for further detail.

@@

1. Clone or download  [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
2. Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine
3. Run `tar_destroy()` to remove any record and caches of existing targets
3. Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
4. You can view a table of all targets in the pipeline by running `targets::tar_meta()`
5. To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:

@@

[^1]: Gould, E., Fraser, H., Parker, T. *et al.* (2023). Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology [Preprint]. Ecology and Evolutionary Biology. https://doi.org/10.32942/X2GG62

>>>>

# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" width="120"/>

@@

> Note that the manuscript source-code for *Gould et al.* is located in a separate repository at <https://github.com/egouldo/ManyAnalysts>, which can be viewed at <https://egouldo.github.io/ManyAnalysts/>.

@@

The data processing and analysis can be freely reproduced with the help of the [`targets::`](https://github.com/ropensci/targets) package.
Please see the documentation at <https://docs.ropensci.org/targets/> for further detail.

@@

1.  Clone or download [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine
3.  Run `tar_destroy()` to remove any record and caches of existing targets
4.  Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
5.  You can view a table of all targets in the pipeline by running `targets::tar_meta()`
6.  To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:

@@

```         
To cite package ‘ManyEcoEvo’ in publications use:

  Gould E, Fraser H, Nakagawa S, Parker T (2023). _ManyEcoEvo: Meta-analyse
  data from 'Many-Analysts' style studies_. R package version 1.0.0,
  <https://github.com/egouldo/ManyEcoEvo>.

A BibTeX entry for LaTeX users is

  @Manual{,
    title = {ManyEcoEvo: Meta-analyse data from 'Many-Analysts' style studies},
    author = {Elliot Gould and Hannah S. Fraser and Shinichi Nakagawa and Timothy H. Parker},
    year = {2023},
    note = {R package version 1.0.0},
    url = {https://github.com/egouldo/ManyEcoEvo},
  }
```

[^1]: Gould, E., Fraser, H., Parker, T.
    *et al.* (2023).
    Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology \[Preprint\].
    Ecology and Evolutionary Biology.
    https://doi.org/10.32942/X2GG62
